This is the title [Article v\versionnumber]

### 2022-09-13 manuscript/manuscript.tex
Add example visualizations, minor text updates

Molecular mechanics based approaches describe the underlying PES through empirically fit force-fields, which reduce the computational demand of these calculations tremendously.
This allows for the treatment of large biological systems such as proteins in aqueous solution.
Implicit solvent methods such as MM/PBSA or MM/GBSA \cite{Sitkoff1994-pbsa,Kollman2000-mmpbsa} can quickly provide results for a large number of structures, but yield inaccurate results when compared to more rigorous explicit solvent methods \cite{Genheden2015-mmpbsa-review}.
On the other hand, the free energy of solvation can be calculated in a statistically rigorous way using explicit solvent simulations combined with alchemical methods such as free energy perturbation (FEP) \cite{Zwanzig1954-reweighting} or thermodynamic integration(TI) \cite{Kirkwood1935-ti}.
However, they are unable to provide a spatial interpretation of the results.
Furthermore, splitting the resulting free energy into contributions for the enthalpy and entropy is challenging \cite{Peter2004-alchemical-entropy}.
%Assuming sufficient sampling, they can accurately predict the free energy of solvation in the boundaries of the assumptions underlying their forcefield. 
%However, the seperation of enthalpic and entropic contributions to the free energy of solvation is difficult with these methods and localizing these contributions not easily possible.

@@

In \software{ccptraj}, the rectangular prism is defined by parameters of the \inlinecode{gist} command.
The center of the grid is defined by \inlinecode{gridcntr}, the dimensions of 
the grid is defined by \inlinecode{griddim} (in voxel counts), and the spacing 
is defined by \inlinecode{gridspacn} (in $\AA$).

@@

It has been shown in literature \cite{Chen2021,Waibl2022-gist-solvents} that the total solvation entropy in water is best approximated by 0.6 times the first order entropy.
Also compute the scaled entropy and check the effect on the binding affinity.
The expected results are summarized in Table~\ref{tab_dg_monomers_dimer}.
%\todo{Table 1 is placed quite akwardly at the moment for me, maybe enforce its position? -vah. Ok? -fwa}
\todo{this table is super confusing to me. What's "total"? Doesn't seem to be E-TS. Diff is also not the sum of other total entries. Shouldn't it be TS instead of S?-vah}
\begin{table}[h]
	\caption{Free energy contributions for the monomers and the dimer in kcal$\cdot$mol$^{-1}$.}\label{tab_dg_monomers_dimer}
	\small
	\begin{tabular}{lrrrrr}
		\toprule
		System       & E(internal) & $\Delta E^\textit{GIST}$ & $\Delta S^\textit{GIST}$ & $\Delta S^\textit{scaled}$ & total \\
		\midrule
		complex      & -1303.4 & -361.2 & -233.1 & -139.9 & -1524.7 \\
		streptavidin & -1180.7 & -360.8 & -242.4 & -145.4 & -1396.1 \\
		biotin       & -24.0   &  -98.1 &  -35.1 &  -21.1 &  -101.0 \\
		Diff         & -98.7   &   97.7 &   44.4 &   26.6 &   -27.6 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{tabular}{l p{.7\textwidth}}
\toprule
doorder & Calculate the water order parameter [reference] for each voxel\\
doeij & Calculate the triangular matrix representing the water-water 
interactions between pairs of voxels.\\
skipE & Skip all energy calculations (cannot be specified with ’doeij’)\\
skipS & Skip all the entropy calculations.\\
refdens <rdval> & Reference density of bulk water, used in computing 
$g_O, g_H$, and the translational entropy. Default is 0.0334 molecules/Å3. \\
temp <tval> & Temperature of the input trajectory. \\
noimage &  Disable distance imaging in energy calculation. \\
gridcntr <xval> <yval> <zval> & Coordinates (Å) of the center of the grid 
(default 0.0, 0.0, 0.0). \\
griddim <xval> <yval> <zval> & Grid dimensions along each coordinate axis 
(default 40, 40, 40).\\
gridspacn <spaceval> & Grid spacing (linear dimension of each voxel) in 
Angstroms. Values greater than 0.75 Å are not recommended (default 0.5 Å).\\
prefix <filename prefix> & Output file name prefix (default “gist”).\\
ext <grid extension> & Output grid file name extension (default “.dx”). \\
out <output> & Name of the main GIST output file. If not specified set to 
’<prefix>-output.dat’.\\
info <info> & Name of main GIST info file. If not specified info is 
written to standard output. \\
\bottomrule
\end{tabular}

\textbf{Output}\\
GIST calculations put out a variety of data sorted by voxel into a file 
specified by the "out" keyword. Some of the output data is also automatically 
written to "open data explorer" (.dx) files for convenient visualisation in 
software such as VMD or PyMOL. The following columns can be found in the output 
file:
\begin{tabular}{l l p{.8\textwidth}}
\toprule
Name & Keyword & Description\\
\midrule
gX & X & For every element in the main solvent, the number density of atoms found in the voxel, in units of the bulk density. If the same element occurs multiple times, the bulk density is scaled accordingly. \\
Esw & X &  Mean solute-water interaction energy density. \\
Eww & X & Mean water-water interaction energy density. \\
PME & [pme] & Water PME energy density. \\
U\_PME & [pme] & Water PME energy density. \\
dTStrans & X & First order translational entropy density. \\
dTSorient & X & First order orientational entropy density . \\
neighbor & X & Mean number of waters neighboring the water molecules found in this voxel multiplied by the voxel number density. \\
dipole & X & Magnitude of mean dipole moment (polarization). \\
order & X & (if \inlinecode{doorder} was specified) Average Tetrahedral Order Parameter. \\
dipolex & X & x-component of the mean water dipole moment density \\
dipoley & X & y-component of the mean water dipole moment density \\
dipolez & X & z-component of the mean water dipole moment density \\
Eij & X & (if \inlinecode{doeij} was specified) Water-water interaction matrix. \\
\bottomrule
\end{tabular}
\end{checklist}
\end{Checklists*}

>>>>

\todo{Remove the part about QM vs.\ MM. We are doing MD and cite ALL solvation methods. COSMO, other implicit solvents, information theory, QSAR, Pratt and coworkers, Mobley and coworkers}
Molecular mechanics based approaches describe the underlying PES through empirically fit force-fields, which reduce the computational demand of these calculations tremendously.
This allows for the treatment of large biological systems such as proteins in aqueous solution.
Implicit solvent methods such as MM/PBSA or MM/GBSA \cite{Sitkoff1994-pbsa,Kollman2000-mmpbsa} can quickly provide results for a large number of structures, but yield inaccurate results when compared to more rigorous explicit solvent methods \cite{Genheden2015-mmpbsa-review}.
On the other hand, the free energy of solvation can be calculated in a statistically rigorous way using explicit solvent simulations combined with alchemical methods such as free energy perturbation (FEP) \cite{Zwanzig1954-reweighting} or thermodynamic integration(TI) \cite{Kirkwood1935-ti}.
However, they are unable to provide a spatial interpretation of the results.
Furthermore, splitting the resulting free energy into contributions for the enthalpy and entropy is challenging \cite{Peter2004-alchemical-entropy}.
%Assuming sufficient sampling, they can accurately predict the free energy of solvation in the boundaries of the assumptions underlying their forcefield. 
%However, the seperation of enthalpic and entropic contributions to the free energy of solvation is difficult with these methods and localizing these contributions not easily possible.

@@

In \software{ccptraj}, the rectangular prism is defined by parameters of the \inlinecode{gist} command.
The center of the grid is defined by \inlinecode{gridcntr}, the dimensions of 
the grid is defined by \inlinecode{griddim} (in voxel counts), and the spacing 
is defined by \inlinecode{gridspacn} (in Å).

@@

It has been shown in literature \cite{Chen2021,Waibl2022-gist-solvents} that the total solvation entropy in water is best approximated by 0.6 times the first order entropy.
Also compute the scaled entropy and check the effect on the binding affinity.
The expected results are summarized in Table~\ref{tab_dg_monomers_dimer}.
%\todo{Table 1 is placed quite akwardly at the moment for me, maybe enforce its position? -vah. Ok? -fwa}
\todo{this table is super confusing to me. What's "total"? Doesn't seem to be E-TS. Diff is also not the sum of other total entries. Shouldn't it be TS instead of S?-vah}
\begin{table}[h]
	\caption{Free energy contributions for the monomers and the dimer in kcal$\cdot$mol$^{-1}$. ``total'' is calculated as $E^\text{internal} + \Delta E^\text{GIST} - \Delta S^\text{scaled}$.}\label{tab_dg_monomers_dimer}
	\small
	\begin{tabular}{@{}lrrrrr@{}}
		\toprule
		System       & E(internal) & $\Delta E^\textit{GIST}$ & $\Delta S^\textit{GIST}$ & $\Delta S^\textit{scaled}$ & total \\
		\midrule
		complex      & -1303.4 & -361.2 & -233.1 & -139.9 & -1524.7 \\
		streptavidin & -1180.7 & -360.8 & -242.4 & -145.4 & -1396.1 \\
		biotin       & -24.0   &  -98.1 &  -35.1 &  -21.1 &  -101.0 \\
		Diff         & -98.7   &   97.7 &   44.4 &   26.6 &   -27.6 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{tabular}{@{}l p{.7\textwidth}@{}}
\toprule
doorder & Calculate the water order parameter [reference] for each voxel\\
doeij & Calculate the triangular matrix representing the water-water 
interactions between pairs of voxels.\\
skipE & Skip all energy calculations (cannot be specified with ’doeij’)\\
skipS & Skip all the entropy calculations.\\
refdens <rdval> & Reference density of bulk water, used in computing 
$g_O, g_H$, and the translational entropy. Default is 0.0334 molecules/Å3. \\
temp <tval> & Temperature of the input trajectory. \\
noimage &  Disable distance imaging in energy calculation. \\
gridcntr <xval> <yval> <zval> & Coordinates (Å) of the center of the grid 
(default 0.0, 0.0, 0.0). \\
griddim <xval> <yval> <zval> & Grid dimensions along each coordinate axis 
(default 40, 40, 40).\\
gridspacn <spaceval> & Grid spacing (linear dimension of each voxel) in 
Angstroms. Values greater than 0.75 Å are not recommended (default 0.5 Å).\\
prefix <filename prefix> & Output file name prefix (default “gist”).\\
ext <grid extension> & Output grid file name extension (default “.dx”). \\
out <output> & Name of the main GIST output file. If not specified set to 
’<prefix>-output.dat’.\\
info <info> & Name of main GIST info file. If not specified info is 
written to standard output. \\
\bottomrule
\end{tabular}

\textbf{Output}\\
GIST calculations put out a variety of data sorted by voxel into a file 
specified by the "out" keyword. Some of the output data is also automatically 
written to "open data explorer" (.dx) files for convenient visualisation in 
software such as VMD or PyMOL. The following columns can be found in the output 
file:
\begin{tabular}{@{}l l p{.8\textwidth}@{}}
\toprule
Name & Keyword & Description\\
\midrule
gX & X & For every element in the main solvent, the number density of atoms found in the voxel, in units of the bulk density. If the same element occurs multiple times, the bulk density is scaled accordingly. \\
Esw & X &  Mean solute-water interaction energy density. \\
Eww & X & Mean water-water interaction energy density. \\
PME & [pme] & Water PME energy density. \\
U\_PME & [pme] & Water PME energy density. \\
dTStrans & X & First order translational entropy density. \\
dTSorient & X & First order orientational entropy density . \\
neighbor & X & Mean number of waters neighboring the water molecules found in this voxel multiplied by the voxel number density. \\
dipole & X & Magnitude of mean dipole moment (polarization). \\
order & X & (if \inlinecode{doorder} was specified) Average Tetrahedral Order Parameter. \\
dipolex & X & x-component of the mean water dipole moment density \\
dipoley & X & y-component of the mean water dipole moment density \\
dipolez & X & z-component of the mean water dipole moment density \\
Eij & X & (if \inlinecode{doeij} was specified) Water-water interaction matrix. \\
\bottomrule
\end{tabular}
\end{checklist}
\end{Checklists*}
